\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-03 paper.tex
added some comments for good places to put more images

ARuko uses augmented reality to translate text at the site as well. While AR
translation apps exist, the experience can be frustrating, and produce poor
results. Google's text recognition and machine-learning powered translation
technology is certainly impressive. At the same time, the translation service
works better in ``scan'' mode instead of ``instant'' mode. In ``instant'' mode,
the app attempts to translate text as quickly as possible, superimposing the
translated text onto the real world using the camera. In ``scan'' mode, the user
first takes a photo. Then, the user is prompted to highlight where text appears
in the photo. After the translation is complete, the translated text appears in
a separate UI element instead superimposed onto the photo. In most cases, it is
more convenient and readable to have the translation appear in a separate
scrollable text box. This motivated the current design of the ``info buttons''
in ARuko. Instead of placing text directly onto signage, we place a blue button
with a stylized `i' in the center. By tapping on this button, a separate UI
element will appear containing the translated text. Since this button is cast
into the world using the AR camera, the button appears to be placed directly
onto the content in the real world.

@@

The last major UI implementation obstacle we had to overcome was a way to keep
audio playing with the phone in your pocket. Atticus insisted that this sort of
feature was required so that users could listen to the audio tour without using
any of the other functionality the app provides, like the image gallery in each
region or the AR features. Despite how common it is for apps to play audio in
the background or while the phone is locked, Unity does not provide a way to
accomplish this. Our workaround was to create a ``pocket mode'' that prevents UI
elements from accidentally being triggered. The user exits pocket mode with a
deliberate swipe to the right. If the slider is released partway through the
action, the slider springs back to the beginning. We were ultimately able to
replicate Atticus's Adobe XD file almost perfectly.

@@

For this project, Atticus sent us the original Unity project files for NOxAR.
We then had to figure out how to turn the original project into a ground plane
AR app. At first we tried importing the assets for the Noh performer into a new
Unity project. We did this for a couple reasons. The first reason was because
we didn't want all of the extra components of the original NOxAR project to
get in the way of what we were trying to do. We also did this because the 
original project was made with a 2017 version of Unity, so we wanted to try to
use our more recent version so we wouldn't risk running into any depricated 
features or functionalities. We did eventually get this method to work, but the
model of the Noh performer was lacking a lot of the details that the original 
model had. This was attributed to poor importation of the original assets, so 
we decided to try making changes to the original NOxAR project instead.

>>>>

ARuko uses augmented reality to translate text at the site as well. While AR
translation apps exist, the experience can be frustrating, and produce poor
results. Google's text recognition and machine-learning powered translation
technology is certainly impressive. At the same time, the translation service
works better in ``scan'' mode instead of ``instant'' mode. In ``instant'' mode,
the app attempts to translate text as quickly as possible, superimposing the
translated text onto the real world using the camera. %could put an image of instant mode here as an example
In ``scan'' mode, the user first takes a photo. Then, the user is prompted to 
highlight where text appears in the photo. %could put an example here as well
After the translation is complete, the translated text appears in a separate UI %another example?
element instead superimposed onto the photo. In most cases, it is more 
convenient and readable to have the translation appear in a separate scrollable
text box. This motivated the current design of the ``info buttons'' in ARuko. 
Instead of placing text directly onto signage, we place a blue button with a 
stylized `i' in the center. By tapping on this button, a separate UI element 
will appear containing the translated text. Since this button is cast into the %example
world using the AR camera, the button appears to be placed directly onto the 
content in the real world.

@@

The last major UI implementation obstacle we had to overcome was a way to keep
audio playing with the phone in your pocket. Atticus insisted that this sort of
feature was required so that users could listen to the audio tour without using %maybe include an image of pocket mode here
any of the other functionality the app provides, like the image gallery in each
region or the AR features. Despite how common it is for apps to play audio in
the background or while the phone is locked, Unity does not provide a way to
accomplish this. Our workaround was to create a ``pocket mode'' that prevents UI
elements from accidentally being triggered. The user exits pocket mode with a
deliberate swipe to the right. If the slider is released partway through the
action, the slider springs back to the beginning. We were ultimately able to
replicate Atticus's Adobe XD file almost perfectly.

@@

For this project, Atticus sent us the original Unity project files for NOxAR.
We then had to figure out how to turn the original project into a ground plane
AR app. At first we tried importing the assets for the Noh performer into a new
Unity project. We did this for a couple reasons. The first reason was because
we didn't want all of the extra components of the original NOxAR project to
get in the way of what we were trying to do. We also did this because the %could probably put an example pic here
original project was made with a 2017 version of Unity, so we wanted to try to
use our more recent version so we wouldn't risk running into any depricated 
features or functionalities. We did eventually get this method to work, but the
model of the Noh performer was lacking a lot of the details that the original 
model had. This was attributed to poor importation of the original assets, so 
we decided to try making changes to the original NOxAR project instead.
